% 8 pages - single blind
\documentclass[conference,letterpaper]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{cite}
\usepackage{svg}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{xcolor}
% \definecolor{TRAIL_pink}{HTML}{FF009D}
% \definecolor{TRAIL_blue}{HTML}{000099}

\definecolor{dark_red}{HTML}{C1272D}
\definecolor{indigo}{HTML}{0000a7}
\definecolor{yellow}{HTML}{eecc16}
\definecolor{teal}{HTML}{008176}
\definecolor{light_gray}{HTML}{b3b3b3}

\usepackage{textcomp}
\usepackage{paralist}

% Encoding
\usepackage[utf8]{inputenc}

% Hyperlinks
\usepackage{url}

% Figures
\usepackage[caption=false,font=footnotesize]{subfig}

% Tables
\usepackage{booktabs}

% Listings
\usepackage{listings}
\lstset{
showspaces=false,
showtabs=false,
breaklines=true,
showstringspaces=false,
tabsize=2,
basicstyle=\tiny\ttfamily,
xleftmargin=1.6em,
escapeinside={<@}{@>},
moredelim=[is][\sout]{|}{|},
frame=tb,
captionpos=b
}

% custom command

% \makeatletter % changes the catcode of @ to 11
% \newcommand{\linebreakand}{%
%   \end{@IEEEauthorhalign}
%   \hfill\mbox{}\par
%   \mbox{}\hfill\begin{@IEEEauthorhalign}
% }
% \makeatother % changes the catcode of @ back to 12

\makeatletter
\newcommand{\linebreakand}{%
  \end{@IEEEauthorhalign}
  \hfill\mbox{}\par
  \mbox{}\hfill\begin{@IEEEauthorhalign}
}

\usepackage{todonotes} %To remove before submission !!!!!
\setlength {\marginparwidth }{2cm}  % Same
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%\title{An Empirical Evaluation of Recommendation Explanations Generated by Large Language Models}

% \title{An Empirical Evaluation of Recommendation Explanations Generated by Large Language Models\\--\\Project Proposal for TRAIL’23 Workshop at Nantes}
\title{User Preferences for Large Language Model versus Template-Based Explanations of Movie Recommendations: A Pilot Study}

\author{
    \IEEEauthorblockN{Julien Albert}
    \IEEEauthorblockA{UNamur\\julien.albert@unamur.be}

    \and

    \IEEEauthorblockN{Martin Balfroid}
    \IEEEauthorblockA{UNamur\\martin.balfroid@unamur.be}   

    \and 

    \IEEEauthorblockN{Miriam Doh}
    \IEEEauthorblockA{ULB-UMONS\\miriam.doh@ulb.be}

    \and

    \IEEEauthorblockN{Jeremie Bogaert}
    \IEEEauthorblockA{UCLouvain\\jeremie.bogaert@uclouvain.be}

    \linebreakand

    \IEEEauthorblockN{Luca La Fisca}
    \IEEEauthorblockA{UMONS\\luca.lafisca@umons.be}

    \and

    \IEEEauthorblockN{Liesbet De Vos}
    \IEEEauthorblockA{UNamur\\liesbet.devos@unamur.be}

    \and

    \IEEEauthorblockN{Bryan Renard}
    \IEEEauthorblockA{Multitel-UNamur\\renard@multitel.be\\bryan.renard@unamur.be}

    \and

    \IEEEauthorblockN{Vincent Stragier}
    \IEEEauthorblockA{UMONS\\vincent.stragier@umons.ac.be}

    \and

    \IEEEauthorblockN{Emmanuel Jean}
    \IEEEauthorblockA{Multitel\\jean@multitel.be}
}

\maketitle

\begin{abstract}

Recommender systems have become integral to our digital experiences, from online shopping to streaming platforms. Still, the rationale behind their suggestions often remains opaque to users. While some systems employ a graph-based approach, offering inherent explainability through paths associating recommended items and seed items, non-experts could not easily understand these explanations. A popular alternative is to convert graph-based explanations into textual ones using a template and an algorithm, which we denote here as “template-based” explanations. Yet, these can sometimes come across as impersonal or uninspiring. A novel method would be to employ large language models (LLMs) for this purpose, which we denote as “LLM-based”. To assess the effectiveness of LLMs in generating more resonant explanations, we conducted a pilot study with 25 participants. They were presented with three explanations: (1) traditional template-based, (2) LLM-based rephrasing of the template output, and (3) purely LLM-based explanations derived from the graph-based explanations. Although subject to high variance, preliminary findings suggest that LLM-based explanations may provide a richer and more engaging user experience, further aligning with user expectations. This study sheds light on the potential limitations of current explanation methods and offers promising directions for leveraging large language models to improve user satisfaction and trust in recommender systems.

\end{abstract}

\begin{IEEEkeywords}
Large Language Models, Recommender Systems, Explainability, GD6
\end{IEEEkeywords}

\input{content/01_introduction}
\input{content/02_implementation}
\input{content/03_user_eval}
\input{content/04_future_works}

% Commented to not break double-blind
\section*{Acknowledgment}
This research was partially supported by the ARIAC project (No. 2010235), funded by the Service Public de Wallonie (SPW Recherche).
This research used resources of the “Plateforme Technologique de Calcul Intensif (PTCI)” (http://www.ptci.unamur.be) located at the University of Namur, Belgium, which is supported  by the FNRS-FRFC, the Walloon Region, and the University of Namur (Conventions No. 2.5020.11, GEQ U.G006.15, 1610468, RW/GEQ2016 et U.G011.22). The PTCI is member of the “Consortium des Équipements de Calcul Intensif  (CÉCI)” (\url{https://www.ceci-hpc.be}).
Vincent Stragier is funded through a PhD grant from the Œuvre fédérale Les Amis des Aveugles et Malvoyants ASBL- The Friends of the Blind and Visually Impaired Federal Charity-, Ghlin, Belgium and the Loterie Nationale, Rue Belliard 25-33, 1040 Brussels, Belgium. Vincent Stragier is partially supported by the FNRS-FRS.
Bryan Renard is funded by the Public Service of Wallonia (Economy, Employment and Research), under the FoodWal agreement n°2210182 from the Win4Excellence project of the Wallonia Recovery Plan.

\bibliographystyle{ieeetr}
\bibliography{references}

% In APA style, the appendices are at the very end of the article
\newpage
\appendix
\input{content/10_shortbios}
\input{content/11_ARIAC_and_TRAIL}

\end{document}
